Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-21 numerical-radiation-homogeneous.tex
clean up

where the constant coefficients $\alpha$, $\beta$, $\gamma$, $z_0$ and
$z_1$ are fits from the literature.  For radiation field types 1-3
(numbered as they appear in the \enzo\ source code and simulation
parameter values), we
give the coefficients for the photoionization (and photo-heating)
rates of H, He, and He$^+$ in Table~\ref{table:homo_coefs}.  Radiation
background types 1
and 2 are based on \citet{1996ApJ...461...20H} with two different
intrinsic quasar spectra slopes, while Type 3 is from
\citet{2012ApJ...746..125H}, modified to match the normalized field
found in \citet{Kirkman05}.  Type 4 is the same as Type 3 but also
adds X-ray Compton heating from \citet{MadauEfstathiou99}, using
equations (4) and (11) of that paper.

@@

Types 8, 9, and 14 have only photo-dissociating Lyman-Werner flux,
with Type 8 being constant and Type 9 using the redshift-dependent
results of \citet{TrentiStiavelli09}.  Type 14 uses a fit from
\citet{WiseAbel05} for the range $6 < z < 50$, constant for $z<6$, and
zero for $z > 50$.  Other types are undefined or unused.

\red{Note: we talk about several radiation field types that are not in
Table~\ref{table:homo_coefs} (4...14).  Do we want to increase the
length of the table, remove the text from the section, or perhaps just
say something in this section about how the table is for illustrative purposes? }

>>>>

where the constant coefficients $\alpha$, $\beta$, $\gamma$, $z_0$ and
$z_1$ are fits from the literature.  For radiation field types 1-3
(numbered as they appear in the \enzo\ source code and simulation
parameter values), we
give the coefficients for the photoionization (and photo-heating)
rates of H, He, and He$^+$ in Table~\ref{table:homo_coefs}.  Radiation
background types 1
and 2 are based on \citet{1996ApJ...461...20H} with two different
intrinsic quasar spectra slopes, while Type 3 is from
\citet{2012ApJ...746..125H}, modified to match the normalized field
found in \citet{Kirkman05}.

The remainder of the radiation field types either build on the fits in Types
1-3 or use a completely different form and therefore we describe them
in the text rather than in Table~\ref{table:homo_coefs}.
Type 4 is the same as Type 3 but also
adds X-ray Compton heating from \citet{MadauEfstathiou99}, using
equations (4) and (11) of that paper.

@@

Types 8, 9, and 14 have only a photo-dissociating Lyman-Werner flux,
with Type 8 being constant and Type 9 using the redshift-dependent
results of \citet{TrentiStiavelli09}.  Type 14 uses a fit from
\citet{WiseAbel05} for the range $6 < z < 50$, constant for $z<6$, and
zero for $z > 50$.  Other types are either undefined or currently unused.
